---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(EnvStats)
library(rootSolve)
library(SpatialExtremes)
library(pracma)
library(expint)
```


```{r}
### Test statistics for Cramer von Mises- and Anderson Darling test for Goodness of fit
W2 <- function(x){
  n <- length(x)
  result <- sum((x - (seq(1, 2 * n - 1, 2) / (2 * n))) ** 2)
  return(result + 1 / (12 * n))
}

A2 <- function(x){
  n <- length(x)
  return(- n - (1 / n) * sum(seq(1, 2 * n - 1, 2) * (log(x) + log(1 - rev(x)))))
}
```


```{r}
### Create a 'print' method for class "gof_test"
print.gof_test <- function(x){
  cat('Results of Goodness-of-Fit Test\n-------------------------------\n\nTest Method:                     ',x$Method,'\n\nNull distribution:               ',x$Distribution,'\n\nSample Size:                     ',x$n,'\n\nEstimated Parameters:            ',x$Estimated,'\n\nParameters (and Estimations):    ',x$Parameters,'\n\nTest Statistic:                  ',x$Statistic_Name,' = ',x$Statistic,'\n\n\nIntervals for H0:\n',x$Critical,'', sep='')
}
```



```{r}
### Distribution functions for the supported distributions
# Extreme value
F_extreme <- function(x, location, scale){
  return(exp(-exp(-(x - location) / scale)))
}

# Generalized Pareto
F_gpd <- function(x, scale, shape){
  return(1 - (1 - shape * x / scale) ** (1 / shape))
}
```


```{r}
### Estimation Functions

# Extreme value
est_extreme <- function(x, param = c(NA,NA)){
  n <- length(x)
  
  # location unknown, scale known, Case 1
  if (is.na(param[1]) == TRUE & is.na(param[2]) != TRUE){
    location <- -param[2] * log(mean(exp(- x / param[2])))
    return(c(location, param[2]))
  }
  
  # location known, scale unknown, Case 2
  if (is.na(param[1]) != TRUE & is.na(param[2]) == TRUE){
    y <- x - param[1]
    estimator <- function(scale){
      return((sum(y) - sum(y * exp(- y / scale))) / n - scale)
    }
    scale <- uniroot(estimator, c(0,100))$root
    return(c(param[1], scale))
  }
  
  # both unknown, Case 3
  if (is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
    estimator <- function(scale){
      return(mean(x) - (sum(x * exp(- x / scale)) / sum(exp(- x / scale))) - scale)
    }
    scale <- uniroot(estimator, c(0.1,100))$root
    location <- - scale * log(1 / n * sum(exp(- x / scale)))
    return(c(location, scale))
  }
}


# Pareto
est_pareto <- function(x, param = c(NA,NA)){
  n <- length(x)
  
  # scale unknown, shape known, Case 1
  if (is.na(param[1]) == TRUE & is.na(param[2]) != TRUE){
    scale <- min(x, na.rm = TRUE)
    return(c(scale, param[2]))
  }
  
  # scale known, shape unknown, Case 2
  if (is.na(param[1]) != TRUE & is.na(param[2]) == TRUE){
    shape <- n / sum(log(x / param[1]))
    return(c(param[1], shape))
  }
  
  # both unknown, Case 3
  if (is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
    scale <- min(x, na.rm = TRUE)
    shape <- n / sum(log(x / scale))
    return(c(scale, shape))
  }
}


# Generalized Pareto
est_gpd <- function(x, param=c(NA,NA)){
  # Parameters given as scale > 0, shape < 1
  n <- length(x)
  
  # scale unknown, shape known, Case 1
  if (is.na(param[1]) == TRUE & is.na(param[2]) != TRUE){
    L <- function(a){
      return(n - (1 - param[2]) * sum(x / (a - param[2] * x)))
    }
    scale <- uniroot(L, c(0.0000001, 0.6), extendInt="yes")$root
    return(c(scale, param[2]))
  }
  
  # scale known, shape unknown, Case 2
  if (is.na(param[1]) != TRUE & is.na(param[2]) == TRUE){
    L <- function(k){
      - n * log(param[1]) - (1 - 1 / k) * sum(log(1 - k * x / param[1]))
    }
    shape <- optimize(L, interval = c(- 100, 0.999999), maximum = TRUE)$maximum
    return(c(param[1], shape))
  }
  
  # both unknown, Case 3
  if (is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
    L <- function(theta){
  return(- n - sum(log(1 - theta * x)) - n * log(- (1 / (n * theta)) * sum(log(1 - theta * x))))
    }
    theta_max <- optimize(L, interval = c(0.0000001, max(x)), maximum = TRUE)$maximum
    shape <- - 1 / n * sum(log(1 - theta_max * x))
    scale <- shape / theta_max
    return(c(scale, shape))
  }
}

# Gamma
est_gamma <- function(x, param = c(NA,NA)){
  # Parameters given as scale > 0, shape > 0
  n <- length(x)
  
  # scale unknown, shape known, Case 1
  if (is.na(param[1]) == TRUE & is.na(param[2]) != TRUE){
    return(sum(x) / (param[2] * n))
  }
  
  # scale known, shape unknown, Case 2
  if (is.na(param[1]) != TRUE & is.na(param[2]) == TRUE){
    return(NA)
  }
  
  # both unknown, Case 3
  if (is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
    return(NA)
  }
}

```




```{r}
### Normal Distribution
# Parameters are given as mu, sigmasq
normal_gof <- function(x, statistic, param = c(NA, NA)){
  x <- sort(x)
  n <- length(x)
  
  # Cramer von Mises
  if(statistic == "cvm"){
    
    # mu unknown, sigma known, Case 1
    if(is.na(param[1]) == TRUE & is.na(param[2]) == FALSE){
      mu_est <- mean(x)
      w = (x - mu_est) / sqrt(param[2])
      Z <- pnorm(w, 0, 1)
      stat <- W2(Z)
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "normal", n = n, Estimated = "mu", Parameters = c(as.character(mu_est),", ",as.character(param[2])), Statistic = stat, Statistic_Name = "W^2", Critical = ".25: [0,.094] ; .15: [0,.117] ; .10: [0,.134] ; .05: [0,.165] ; .025: [0,.197] ; .01: [0,.238] ; .005: [0,.270] ; .0.0025: [0,.302]")
      class(out) <- "gof_test"
      return(out)
    }
    
    # mu known, sigma unknown, Case 2
    if(is.na(param[1]) == FALSE & is.na(param[2]) == TRUE){
      s1sq <- sum((x - param[1])**2) / n
      w <- (x - param[1]) / sqrt(s1sq)
      Z <- pnorm(w, 0, 1)
      stat <- W2(Z)
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "normal", n = n, Estimated = "sigma^2", Parameters = c(as.character(param[1]),", ",as.character(s1sq)), Statistic = stat, Statistic_Name = "W^2", Critical = ".25: [0,.190] ; .15: [0,.263] ; .10: [0,.327] ; .05: [0,.442] ; .025: [0,.562] ; .01: [0,.725] ; .005: [0,.851] ; .0.0025: [0,.978]")
      class(out) <- "gof_test"
      return(out)
    }
    
    # both unknown, Case 3
    if(is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
      mu_est <- mean(x)
      ssq <- var(x)
      w <- (x - mu_est) / sqrt(ssq)
      Z <- pnorm(w, 0, 1)
      stat <- W2(Z) * (1 + 0.5 / n)
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "normal", n = n, Estimated = "mu, sigma^2", Parameters = c(as.character(mu_est),", ",as.character(ssq)), Statistic = stat, Statistic_Name = "W^2", Critical = ".25: [0,.074] ; .15: [0,.091] ; .10: [0,.104] ; .05: [0,.126] ; .025: [0,.148] ; .01: [0,.179] ; .005: [0,.201]")
      class(out) <- "gof_test"
      return(out)
    } 
  }
    


  # Anderson Darling
  if(statistic == "ad"){
    
    # mu unknown, sigma known, Case 1
    if(is.na(param[1]) == TRUE & is.na(param[2]) == FALSE){
      mu_est <- mean(x)
      w = (x - mu_est) / sqrt(param[2])
      Z <- pnorm(w, 0, 1)
      stat <- A2(Z)
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "normal", n = n, Estimated = "mu", Parameters = c(as.character(mu_est),", ",as.character(param[2])), Statistic = stat, Statistic_Name = "A^2", Critical = ".25: [0,.644] ; .15: [0,.782] ; .10: [0,.894] ; .05: [0,1.087] ; .025: [0,1.285] ; .01: [0,1.551] ; .005: [0,1.756] ; .0.0025: [0,1.964]")
      class(out) <- "gof_test"
      return(out)
      }
    
    # mu known, sigma unknown, Case 2
    if(is.na(param[1]) == FALSE & is.na(param[2]) == TRUE){
      s1sq <- sum((x - param[1])**2) / n
      w <- (x - param[1]) / sqrt(s1sq)
      Z <- pnorm(w, 0, 1)
      stat <- A2(Z)
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "normal", n = n, Estimated = "sigma^2", Parameters = c(as.character(param[1]),", ",as.character(s1sq)), Statistic = stat, Statistic_Name = "A^2", Critical = ".25: [0,1.072] ; .15: [0,1.430] ; .10: [0,1.743] ; .05: [0,2.308] ; .025: [0,2.898] ; .01: [0,3.702] ; .005: [0,4.324] ; .0.0025: [0,4.954]")
      class(out) <- "gof_test"
      return(out)
      }
    
    # both unknown, Case 3
    if(is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
      mu_est <- mean(x)
      ssq <- var(x)
      w <- (x - mu_est) / sqrt(ssq)
      Z <- pnorm(w, 0, 1)
      stat <- A2(Z) * (1 + 0.75 / n + 2.25 / (n**2))
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "normal", n = n, Estimated = "mu, sigma^2", Parameters = c(as.character(mu_est),", ",as.character(ssq)), Statistic = stat, Statistic_Name = "A^2", Critical = ".25: [0,.470] ; .15: [0,.561] ; .10: [0,.631] ; .05: [0,.752] ; .025: [0,.873] ; .01: [0,1.035] ; .005: [0,1.159]")
      class(out) <- "gof_test"
      return(out)
          }   
  }
}
```

```{r}
### Exponential distribution
exp_gof <- function(x, statistic) {
  x <- sort(x)
  n <- length(x)
  
  # Cramer von Mises
  if(statistic == "cvm"){
    
    # Lambda not known, Case 1
    lambda_est <- 1 / mean(x)
    Z <- pexp(x, rate = lambda_est)
    stat <- W2(Z) * (1 + 0.16 / n)
    out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "exponential", n = n, Estimated = "lambda", Parameters = as.character(lambda_est), Statistic = stat, Statistic_Name = "W^2", Critical = ".25: [0,.116] ; .15: [0,.148] ; .10: [0,.175] ; .05: [0,.222] ; .025: [0,.271] ; .01: [0,0.338] ; .005: [0,0.390]")
    class(out) <- "gof_test"
    return(out)
    }

  # Anderson Darling
  if(statistic == "ad"){
    
    # Lambda not known, Case 1
    lambda_est <- 1 / mean(x)
    Z <- pexp(x, rate = lambda_est)
    stat <- A2(Z) * (1 + 0.6 / n)
    out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "exponential", n = n, Estimated = "lambda", Parameters = as.character(lambda_est), Statistic = stat, Statistic_Name = "A^2", Critical = ".25: [0,.736] ; .15: [0,.916] ; .10: [0,1.062] ; .05: [0,1.321] ; .025: [0,1.591] ; .01: [0,1.959] ; .005: [0,2.244]")
    class(out) <- "gof_test"
    return(out)
  }
}
```


```{r}
### Extreme-value Distribution
# Parameters are given as location, scale (alpha, beta)
extreme_gof <- function(x, statistic, param = c(NA, NA)){
  x <- sort(x)
  n <- length(x)
  
  # Cramer von Mises
  if(statistic == "cvm"){
    
    # location unknown, scale known, Case 1
    if(is.na(param[1]) == TRUE & is.na(param[2]) == FALSE){
      location <- est_extreme(x, c(NA, param[2]))[1]
      Z <- F_extreme(x, location, param[2])
      stat <- W2(Z) * (1 + 0.16 / n)
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Extreme Value", n = n, Estimated = "location", Parameters = c(as.character(location),", ",as.character(param[2])), Statistic = stat, Statistic_Name = "W^2", Critical = ".25: [0,.116] ; .10: [0,.175] ; .05: [0,.222] ; .025: [0,.271] ; .01: [0,.338]")
      class(out) <- "gof_test"
      return(out)
    }
    
    # location known, scale unknown, Case 2
    if(is.na(param[1]) == FALSE & is.na(param[2]) == TRUE){
      scale <- est_extreme(x, c(param[1],NA))[2]
      Z <- F_extreme(x, param[1], scale)
      stat <- W2(Z) 
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Extreme Value", n = n, Estimated = "scale", Parameters = c(as.character(param[1]),", ",as.character(scale)), Statistic = stat, Statistic_Name = "W^2", Critical = ".25: [0,.186]; .10: [0,.320] ; .05: [0,.431] ; .025: [0,.547] ; .01: [0,.705]")
      class(out) <- "gof_test"
      return(out)
    }
    
    # both unknown, Case 3
    if(is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
      location <- est_extreme(x)[1]
      scale <- est_extreme(x)[2]
      Z <- F_extreme(x, location, scale)
      stat <- W2(Z) * (1 + 0.2 / sqrt(n))
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Extreme Value", n = n, Estimated = "location, scale", Parameters = c(as.character(location),", ",as.character(scale)), Statistic = stat, Statistic_Name = "W^2", Critical = ".25: [0,.073]; .10: [0,.102] ; .05: [0,.124] ; .025: [0,.146] ; .01: [0,.175]")
      class(out) <- "gof_test"
      return(out)
    } 
  }
    


  # Anderson Darling
  if(statistic == "ad"){
    
    # location unknown, scale known, Case 1
    if(is.na(param[1]) == TRUE & is.na(param[2]) == FALSE){
      location <- est_extreme(x, c(NA, param[2]))[1]
      Z <- F_extreme(x, location, param[2])
      stat <- A2(Z) * (1 + 0.3 / n)
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Extreme Value", n = n, Estimated = "location", Parameters = c(as.character(location),", ",as.character(param[2])), Statistic = stat, Statistic_Name = "A^2", Critical = ".25: [0,.736]; .10: [0,1.062] ; .05: [0,1.321] ; .025: [0,1.591] ; .01: [0,1.959]")
      class(out) <- "gof_test"
      return(out)
    }
    
    # location known, scale unknown, Case 2
    if(is.na(param[1]) == FALSE & is.na(param[2]) == TRUE){
      scale <- est_extreme(x, c(param[1],NA))[2]
      Z <- F_extreme(x, param[1], scale)
      stat <- A2(Z) 
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Extreme Value", n = n, Estimated = "scale", Parameters = c(as.character(param[1]),", ",as.character(scale)), Statistic = stat, Statistic_Name = "A^2", Critical = ".25: [0,.1.06]; .10: [0,.1.725] ; .05: [0,2.277] ; .025: [0,2.854] ; .01: [0,3.640]")
      class(out) <- "gof_test"
      return(out)
    }
    
    # both unknown, Case 3
    if(is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
      location <- est_extreme(x, c(NA, NA))[1]
      scale <- est_extreme(x, c(NA, NA))[2]
      Z <- F_extreme(x, location, scale)
      stat <- A2(Z) * (1 + 0.2 / sqrt(n)) 
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Extreme Value", n = n, Estimated = "location, scale", Parameters = c(as.character(location),", ",as.character(scale)), Statistic = stat, Statistic_Name = "A^2", Critical = ".25: [0,.474]; .10: [0,.637] ; .05: [0,.757] ; .025: [0,.877] ; .01: [0,1.038]")
      class(out) <- "gof_test"
      return(out)
    } 
  }
}
```


```{r}
### Weibull
# Parameters are given as scale, shape (beta, k)
# Just perform a transformation to get an extreme value distribution, then call       
# the function extreme_gof
weibull_gof <- function(x, statistic, param = c(NA, NA)){
  x <- sort(x)
  n <- length(x)
  y <- sort(-log(x))
  
  
  # Cramer von Mises
  if(statistic == "cvm"){
    
    # scale unknown, shape known, Case 1
    if(is.na(param[1]) == TRUE & is.na(param[2]) == FALSE){
    extreme_value_trans <- extreme_gof(y, "cvm", c(NA, 1 / param[2]))
    scale <- exp(as.numeric(extreme_value_trans$Parameters[1]))
    result <- extreme_value_trans$Statistic
    out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Weibull", n = n, Estimated = "scale", Parameters = c(as.character(scale),", ",as.character(param[2])), Statistic = result, Statistic_Name = "W^2", Critical = ".25: [0,.116] ; .10: [0,.175] ; .05: [0,.222] ; .025: [0,.271] ; .01: [0,.338]")
      class(out) <- "gof_test"
      return(out)
    }
    
    # scale known, shape unknown, Case 2
    if(is.na(param[1]) == FALSE & is.na(param[2]) == TRUE){
    extreme_value_trans <- extreme_gof(y, "cvm", c(- log(1 / param[1]), NA))
    shape <- 1 / as.numeric(extreme_value_trans$Parameters[3])
    result <- extreme_value_trans$Statistic
    out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Weibull", n = n, Estimated = "shape", Parameters = c(as.character(param[1]),", ",as.character(shape)), Statistic = result, Statistic_Name = "W^2", Critical = ".25: [0,.186]; .10: [0,.320] ; .05: [0,.431] ; .025: [0,.547] ; .01: [0,.705]")
      class(out) <- "gof_test"
      return(out)
    }
    
    # both unknown, Case 3
    if(is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
      extreme_value_trans <- extreme_gof(y, "cvm", c(NA,NA))
      scale <- exp(as.numeric(extreme_value_trans$Parameters[1]))
      shape <- 1 / as.numeric(extreme_value_trans$Parameters[3])
      result <- extreme_value_trans$Statistic
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Weibull", n = n, Estimated = "scale, shape", Parameters = c(as.character(scale),", ",as.character(shape)), Statistic = result, Statistic_Name = "W^2", Critical = ".25: [0,.073]; .10: [0,.102] ; .05: [0,.124] ; .025: [0,.146] ; .01: [0,.175]")
      class(out) <- "gof_test"
      return(out)
    } 
  }
    


  # Anderson Darling
  if(statistic == "ad"){
    
    # scale unknown, shape known, Case 1
    if(is.na(param[1]) == TRUE & is.na(param[2]) == FALSE){
    extreme_value_trans <- extreme_gof(y, "ad", c(NA, 1 / param[2]))
    scale <- exp(as.numeric(extreme_value_trans$Parameters[1]))
    result <- extreme_value_trans$Statistic
    out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Weibull", n = n, Estimated = "scale", Parameters = c(as.character(scale),", ",as.character(param[2])), Statistic = result, Statistic_Name = "A^2", Critical = ".25: [0,.736]; .10: [0,1.062] ; .05: [0,1.321] ; .025: [0,1.591] ; .01: [0,1.959]")
      class(out) <- "gof_test"
      return(out)
    }
    
    # scale known, shape unknown, Case 2
    if(is.na(param[1]) == FALSE & is.na(param[2]) == TRUE){
    extreme_value_trans <- extreme_gof(y, "ad", c(- log(1 / param[1]), NA))
    shape <- 1 / as.numeric(extreme_value_trans$Parameters[3])
    result <- extreme_value_trans$Statistic
    out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Weibull", n = n, Estimated = "shape", Parameters = c(as.character(param[1]),", ",as.character(shape)), Statistic = result, Statistic_Name = "A^2", Critical = ".25: [0,.1.06]; .10: [0,.1.725] ; .05: [0,2.277] ; .025: [0,2.854] ; .01: [0,3.640]")
      class(out) <- "gof_test"
      return(out)
    }
    
    # both unknown, Case 3
    if(is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
      extreme_value_trans <- extreme_gof(y, "ad", c(NA,NA))
      scale <- exp(as.numeric(extreme_value_trans$Parameters[1]))
      shape <- 1 / as.numeric(extreme_value_trans$Parameters[3])
      result <- extreme_value_trans$Statistic
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Weibull", n = n, Estimated = "scale, shape", Parameters = c(as.character(scale),", ",as.character(shape)), Statistic = result, Statistic_Name = "A^2", Critical = ".25: [0,.474]; .10: [0,.637] ; .05: [0,.757] ; .025: [0,.877] ; .01: [0,1.038]")
      class(out) <- "gof_test"
      return(out)
    } 
  }
}
```


```{r}
### Pareto
# Parameters are given as scale, shape (xmin, alpha)
# Just perform a transformation to get an exponential value distribution, then call     
# the function exponential_gof
# Can only implement Case 2 atm. Case 1 and 3 should not give accurate critical values
# as the transformation depends on estimated parameter
pareto_gof <- function(x, statistic, param){
  x <- sort(x)
  n <- length(x)
  
  # Cramer von Mises
  if(statistic == "cvm"){
    
    # scale known, shape unknown, Case 2
      y <- log(x / param)
      exp_trans <- exp_gof(y, "cvm")
      shape <- exp_trans$Parameters
      result <- exp_trans$Statistic
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Pareto", n = n, Estimated = "shape", Parameters = c(as.character(param),", ",as.character(shape)), Statistic = result, Statistic_Name = "W^2", Critical = ".25: [0,.116] ; .15: [0,.148] ; .10: [0,.175] ; .05: [0,.222] ; .025: [0,.271] ; .01: [0,0.338] ; .005: [0,0.390]")
      class(out) <- "gof_test"
      return(out)
  }
    

  # Anderson Darling
  if(statistic == "ad"){
    
    # scale known, shape unknown, Case 2
      y <- log(x / param)
      exp_trans <- exp_gof(y, "ad")
      shape <- exp_trans$Parameters
      result <- exp_trans$Statistic
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Pareto", n = n, Estimated = "shape", Parameters = c(as.character(param),", ",as.character(shape)), Statistic = result, Statistic_Name = "A^2", Critical = ".25: [0,.736] ; .15: [0,.916] ; .10: [0,1.062] ; .05: [0,1.321] ; .025: [0,1.591] ; .01: [0,1.959] ; .005: [0,2.244]")
      class(out) <- "gof_test"
      return(out)
  }
}
```



```{r}
### Generalized Pareto distribution
# Parameters are given as scale, shape (a,k)
# Atm, Case 3 runs into computational errors that should (probably) not occur.
# Case 2 only works for negative shapes which is undesirable. 
gpd_gof <- function(x, statistic, param = c(NA, NA)){
  x <- sort(x)
  n <- length(x)
  
  # Cramer von Mises
  if(statistic == "cvm"){
    
    # scale unknown, shape known, Case 1
    if(is.na(param[1]) == TRUE & is.na(param[2]) == FALSE){
      scale_est <- est_gpd(x, param = c(NA, param[2]))[1]
      Z <- F_gpd(x, scale_est, param[2])
      stat <- W2(Z)
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Generalized Pareto", n = n, Estimated = "scale", Parameters = c(as.character(scale_est),", ",as.character(param[2])), Statistic = stat, Statistic_Name = "W^2", Critical = "https://www.tandfonline.com/doi/pdf/10.1198/00401700152672573?casa_token=FKsCzUZmFBYAAAAA:jAf6TceZfULvHuXR3_fu80ykBxgiNhzxTumiQVVFL_iUbUt0Uw_SVawlOFml_cQcp0EXg6IJgkJH")
      class(out) <- "gof_test"
      return(out)
    }
    
    # scale known, shape unknown, Case 2
    if(is.na(param[1]) == FALSE & is.na(param[2]) == TRUE){
      shape_est <- est_gpd(x, param = c(param[1], NA))[2]
      Z <- F_gpd(x, param[1], shape_est)
      stat <- W2(Z)
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Generalized Pareto", n = n, Estimated = "shape", Parameters = c(as.character(param[1]),", ",as.character(shape_est)), Statistic = stat, Statistic_Name = "W^2", Critical = "https://www.tandfonline.com/doi/pdf/10.1198/00401700152672573?casa_token=FKsCzUZmFBYAAAAA:jAf6TceZfULvHuXR3_fu80ykBxgiNhzxTumiQVVFL_iUbUt0Uw_SVawlOFml_cQcp0EXg6IJgkJH")
      class(out) <- "gof_test"
      return(out)
    }
    
    # both unknown, Case 3
    if(is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
      scale_est <- est_gpd(x, param = c(NA, NA))[1]
      shape_est <- est_gpd(x, param = c(NA, NA))[2]
      Z <- F_gpd(x, scale_est, shape_est)
      stat <- W2(Z)
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Generalized Pareto", n = n, Estimated = "scale, shape", Parameters = c(as.character(scale_est),", ",as.character(shape_est)), Statistic = stat, Statistic_Name = "W^2", Critical = "https://www.tandfonline.com/doi/pdf/10.1198/00401700152672573?casa_token=FKsCzUZmFBYAAAAA:jAf6TceZfULvHuXR3_fu80ykBxgiNhzxTumiQVVFL_iUbUt0Uw_SVawlOFml_cQcp0EXg6IJgkJH")
      class(out) <- "gof_test"
      return(out)
    }
  }
    


  # Anderson Darling
  if(statistic == "ad"){
    
    
    # scale unknown, shape known, Case 1
    if(is.na(param[1]) == TRUE & is.na(param[2]) == FALSE){
      scale_est <- est_gpd(x, param = c(NA, param[2]))[1]
      Z <- F_gpd(x, scale_est, param[2])
      stat <- A2(Z)
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Generalized Pareto", n = n, Estimated = "scale", Parameters = c(as.character(scale_est),", ",as.character(param[2])), Statistic = stat, Statistic_Name = "A^2", Critical = "https://www.tandfonline.com/doi/pdf/10.1198/00401700152672573?casa_token=FKsCzUZmFBYAAAAA:jAf6TceZfULvHuXR3_fu80ykBxgiNhzxTumiQVVFL_iUbUt0Uw_SVawlOFml_cQcp0EXg6IJgkJH")
      class(out) <- "gof_test"
      return(out)
    }
    
    # scale known, shape unknown, Case 2
    if(is.na(param[1]) == FALSE & is.na(param[2]) == TRUE){
      shape_est <- est_gpd(x, param = c(param[1], NA))[2]
      Z <- F_gpd(x, param[1], shape_est)
      stat <- A2(Z)
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Generalized Pareto", n = n, Estimated = "shape", Parameters = c(as.character(param[1]),", ",as.character(shape_est)), Statistic = stat, Statistic_Name = "A^2", Critical = "https://www.tandfonline.com/doi/pdf/10.1198/00401700152672573?casa_token=FKsCzUZmFBYAAAAA:jAf6TceZfULvHuXR3_fu80ykBxgiNhzxTumiQVVFL_iUbUt0Uw_SVawlOFml_cQcp0EXg6IJgkJH")
      class(out) <- "gof_test"
      return(out)
    }
    
    # both unknown, Case 3
    if(is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
      scale_est <- est_gpd(x, param = c(NA, NA))[1]
      shape_est <- est_gpd(x, param = c(NA, NA))[2]
      Z <- F_gpd(x, scale_est, shape_est)
      stat <- A2(Z)
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Generalized Pareto", n = n, Estimated = "scale, shape", Parameters = c(as.character(scale_est),", ",as.character(shape_est)), Statistic = stat, Statistic_Name = "A^2", Critical = "https://www.tandfonline.com/doi/pdf/10.1198/00401700152672573?casa_token=FKsCzUZmFBYAAAAA:jAf6TceZfULvHuXR3_fu80ykBxgiNhzxTumiQVVFL_iUbUt0Uw_SVawlOFml_cQcp0EXg6IJgkJH")
      class(out) <- "gof_test"
      return(out)
    }
  }
}
```



```{r}
### Gamma
# Parameters are given as scale, shape (beta, m)
gamma_gof <- function(x, statistic, param = c(NA, NA)){
  x <- sort(x)
  n <- length(x)
  
  # Cramer von Mises
  if(statistic == "cvm"){
    
    # scale unknown, shape known, Case 1
    if(is.na(param[1]) == TRUE & is.na(param[2]) == FALSE){
      scale_est <- est_gamma(x, param = c(NA, param[2]))
      Z <- pgamma(x, scale = scale_est, shape = param[2])
      W <- W2(Z)
      result <- W
      if (param[2] == 1){
        result <- W * (1 + 0.16 / n)
      }
      if (param[2] >= 2){
        result <- (1.8 * n * W - 0.14) / (1.8 * n - 1)
      }
    out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Gamma", n = n, Estimated = "scale", Parameters = c(as.character(scale_est),", ",as.character(param[2])), Statistic = result, Statistic_Name = "W^2", Critical = "check documentation for critical values")
      class(out) <- "gof_test"
      return(out)
    }
    
    # scale known, shape unknown, Case 2
    if(is.na(param[1]) == FALSE & is.na(param[2]) == TRUE){
      L <- function(m){
        (m - 1) * sum(log(x)) - sum(x / param[1]) - n * m * log(param[1]) - n * log(gamma(m))
      }
      shape_est <- optimize(L, c(0.00001, 100), maximum = TRUE)$maximum
      Z <- pgamma(x, scale = param[1], shape = shape_est)
      result <- W2(Z)
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Gamma", n = n, Estimated = "shape", Parameters = c(as.character(param[1]),", ",as.character(shape_est)), Statistic = result, Statistic_Name = "W^2", Critical = "check documentation for critical values")
      class(out) <- "gof_test"
      return(out)
    }
    
    # both unknown, Case 3
    if(is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
      L <- function(m){
        (m - 1) * sum(log(x)) - n * m - n * m * log(sum(x / (m * n))) - n * log(gamma(m))
      }
      shape_est <- optimize(L, c(0.00001, 100), maximum = TRUE)$maximum
      scale_est <- mean(x) / shape_est
      Z <- pgamma(x, scale = scale_est, shape = shape_est)
      result <- W2(Z)
      out <- list(Method = "Cramér-von Mises Test for Goodness-of-Fit", Distribution = "Gamma", n = n, Estimated = "scale, shape", Parameters = c(as.character(scale_est),", ",as.character(shape_est)), Statistic = result, Statistic_Name = "W^2", Critical = "check documentation for critical values")
      class(out) <- "gof_test"
      return(out)
    } 
  }
    


  # Anderson Darling
  if(statistic == "ad"){
    
    # scale unknown, shape known, Case 1
    if(is.na(param[1]) == TRUE & is.na(param[2]) == FALSE){
    scale_est <- est_gamma(x, param = c(NA, param[2]))
      Z <- pgamma(x, scale = scale_est, shape = param[2])
      A <- A2(Z)
      result <- A
      if (param[2] == 1){
        result <- A * (1 + 0.6 / n)
      }
      if (param[2] >= 2){
        result <- A + (1 / n) * (0.2 + (0.3 / param[2]))
      }
    out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Gamma", n = n, Estimated = "scale", Parameters = c(as.character(scale_est),", ",as.character(param[2])), Statistic = result, Statistic_Name = "A^2", Critical = "check documentation for critical values")
      class(out) <- "gof_test"
      return(out)
    }
    
    # scale known, shape unknown, Case 2
    if(is.na(param[1]) == FALSE & is.na(param[2]) == TRUE){
      L <- function(m){
        (m - 1) * sum(log(x)) - sum(x / param[1]) - n * m * log(param[1]) - n * log(gamma(m))
      }
      shape_est <- optimize(L, c(0.00001, 100), maximum = TRUE)$maximum
      Z <- pgamma(x, scale = param[1], shape = shape_est)
      result <- A2(Z)
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Gamma", n = n, Estimated = "shape", Parameters = c(as.character(param[1]),", ",as.character(shape_est)), Statistic = result, Statistic_Name = "A^2", Critical = "check documentation for critical values")
      class(out) <- "gof_test"
      return(out)
    }
    
    # both unknown, Case 3
    if(is.na(param[1]) == TRUE & is.na(param[2]) == TRUE){
      L <- function(m){
        (m - 1) * sum(log(x)) - n * m - n * m * log(sum(x / (m * n))) - n * log(gamma(m))
      }
      shape_est <- optimize(L, c(0.00001, 100), maximum = TRUE)$maximum
      scale_est <- mean(x) / shape_est
      Z <- pgamma(x, scale = scale_est, shape = shape_est)
      result <- A2(Z)
      out <- list(Method = "Anderson-Darling Test for Goodness-of-Fit", Distribution = "Gamma", n = n, Estimated = "scale, shape", Parameters = c(as.character(scale_est),", ",as.character(shape_est)), Statistic = result, Statistic_Name = "A^2", Critical = "check documentation for critical values")
      class(out) <- "gof_test"
      return(out)
    }
  }
}

```


```{r message=FALSE, warning=FALSE}
values <- rep(0, 10000)
for(i in 1:10000){
  sim <- rgamma(1000, scale = 0.5, shape = 2)
  values[i] <- gamma_gof(sim, "cvm", param = c(NA, 2))$Statistic
}
```


```{r}
length(values[values > .156]) / length(values)
```


Check values
Normal
cvm Case1: good Case2: good Case 3: good
ad Case1: good Case2: good Case2: good
Exponential
cvm Case1: good
ad Case1: good
Extreme Value
cvm Case 1: good Case 2: good Case 3: good
as Case 1: good Case 2: good Case 3: good
Weibull
cvm Case 1: good Case 2: good Case 3: good
ad Case 1: good Case 2: good Case 3: good
Pareto
cvm Case 2: good
ad Case 2: good
GPD
cvm Case 1: good (only negative shape) Case 2: good Case 3: bad
ad Case 1: good (only negative values) Case 2: good Case 3: bad
Gamma
cvm Case 1: 

Try to fix bad cases by using optimize instead of uniroot.

Use Gamma and extreme value distributions to derive tests for special cases, in particular Gumbel.


```{r}
sim <- rgamma(1000, scale = 3, shape = 14)
gamma_gof(sim, "cvm", param = c(NA, NA))
```


